Mutual Modeling in Human-Robot Interaction - Scientific part

### 2014-03-20 project-mutual-modeling.tex
Added the biblio
Added sections on robotic + theory of mind, false belief

@@

The content of mutual models ranges from 'dispositional' versus 'situational'
aspects. The 'dispositional' aspects refer to A's representation of B's long
term knowledge, skills or traits. It is thus closely related to the notion of
transactive memory (Wegner, 1987; Moreland, 2000). 'Situational' aspects refer
to A's representation of B's knowledge, behavior or intentions specifically
activated in the situation in which A and B are collaborating, some of them
being valid for 2 seconds, other ones for 2 hours. Here are examples of
fragments that constitute A's model of B regarding to aspects X, noted
$Model(A,B,X)$:

@@

\subsubsection{Simple model of mutual modeling}

To report experiments on MM, we use a simple notational system: "A knows that B
knows X", noted \model{A}{B}{X} is a simplistic but hopefully useful reduction to
reason on mutual modeling. This notation does not mean A as an explicit,
monolithic representation of B: It is an abstraction referring to complex
socio-cognitive processes.

We refer to the degree of accuracy of the mutual model as
\Model{A}{B}{X}. To estimate, the MM effort, we need 3 variables.

@@

@@

\begin{itemize}
    \item $\mathcal{H}_{1}$: $\mathcal{M}^{\circ}(A,B)$ depends upon A’s ability or effort
        to model B,

    \item $\mathcal{H}_{2}$: $\mathcal{M}^{\circ}(A,B)$ depends upon  B’s ability of
        effort to help A to model him/herself

@@

>>>>

Human-robot interaction is a challenge for artificial intelligence. This field
indeed lays at the crossroad of several other domains of AI and requires to
tackle them in a holistic manner: Modeling humans and human cognition;
acquiring, representing, manipulating in a tractable way abstract knowledge;
reasoning on this knowledge to make decisions; and eventually instantiating
those decisions into physical actions in coordination with humans. Many AI
techniques are invited, from visual processing to symbolic reasoning, from task
planning to \emph{theory of mind} building, from reactive control to action
recognition and learning.

\paragraph{Theory of Mind}

Theory of Mind (originally defined in~\cite{premack1978does}) is the cognitive
ability that a subject possesses to represent the mental state of another
agent, possibly including knowledge that contradicts the subject's own model: for
example, a book can be at the same time \emph{visible} for myself, and \emph{not
visible} for you.

Children develop this skill, which is essential to understand others'
perspectives during interactions, around the age of three. It supposes the
ability to build, store and retrieve separate models of the knowledge of the
interactors.

One classical application of this cognitive skill is the so-called
\emph{False-Belief} experiment (also known as the \emph{Sally and Ann}
experiment)~\cite{Leslie2000}: a child is asked to watch a scene where two
people, A and B, manipulate objects. Then A leaves and B hides away one
object. When A comes back, we ask the child ``where do you think A will
look for the object?''. Before acquiring a theory of mind, children are not
able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false
beliefs} on the world (A still thinks the object is at its original
position since he did not see B hiding it).

@@

The content of mutual models ranges from 'dispositional' versus 'situational'
aspects. The 'dispositional' aspects refer to A's representation of B's long
term knowledge, skills or traits. It is thus closely related to the notion of
transactive memory~\cite{wegner1987transactive, moreland1999transactive}.
'Situational' aspects refer to A's representation of B's knowledge, behavior or
intentions specifically activated in the situation in which A and B are
collaborating, some of them being valid for 2 seconds, other ones for 2 hours.
Here are examples of fragments that constitute A's model of B regarding to
aspects X, noted $Model(A,B,X)$:

@@

The core research question we want to address in this project is
$(\mathcal{Q}_1)$ how mutual modeling impacts the quality of the human-robot
interaction?  \emph{Quality}, in our context, is measured as the performance of
the human-robot pair in selected joint tasks.

To actually instigate a mutual modeling situation, three other research
questions must be addressed. $(\mathcal{Q}_2)$ how can the robot acquire and
represent a mental model of its partners? $(\mathcal{Q}_3)$ conversely, how do
the human partners model the robot and what are the robot's design/behavioural
factors that influences it? $(\mathcal{Q}_4)$ once the robot detects
misunderstandings, what should be the interaction strategy?
\subsubsection{A theoretical model of mutual modeling}

To report experiments on MM, we use a simple notational system: ``A knows that B
knows X", noted \model{A}{B}{X}. This is a simple but hopefully useful reduction to
reason on mutual modeling. This notation does not mean A has an explicit,
monolithic representation of B: it must be understood as an abstraction referring to complex
socio-cognitive processes.

We refer to the degree of accuracy of the mutual model as
\Model{A}{B}{X}. To estimate the MM effort, we need 3 variables.

@@

\subsubsection{Studies}

@@

\begin{itemize}
    \item $\mathcal{H}_{1}$: $\mathcal{M}^{\circ}(A,B)$ depends upon A's ability or effort
        to model B,

    \item $\mathcal{H}_{2}$: $\mathcal{M}^{\circ}(A,B)$ depends upon  B's ability of
        effort to help A to model him/herself

@@

\bibliographystyle{abbrv}
\bibliography{biblio}
